Component response rate variation underlies the stability of complex systems

### 2020-03-22 notebook/SI.Rmd
Add the different gamma distribution stability results to the SI

The same 100000 $\mathbf{M}$ matrices were used to investigate stability when applying each of these different distributions of $\gamma$ values. The table below shows the number of $\mathbf{M}$ that were unstable (_unst) and stable (_stbl) for the exponential (Exp), beta, and gamma distributions.

```{r, echo = FALSE}
fourdists <- read.csv(file = "sim_results/different_distr/four_distr_rand.csv");
kable(fourdists);
```

>>>>

The stability of $\mathbf{A}$ versus $\mathbf{M}$ was investigated for each of the distributions of $\gamma$ shown in panels b-d above. The table below shows the number of $\mathbf{A}$ versus $\mathbf{M}$ that were stable for the exponential (exp), beta, and gamma distributions.

```{r, echo = FALSE}
g_dsts <- read.csv("../inst/extdata/g_dsts.csv");
kable(g_dsts);
```

### 2020-03-22 notebook/SI.tex
Add the different gamma distribution stability results to the SI

The same 100000 \(\mathbf{M}\) matrices were used to investigate
stability when applying each of these different distributions of
\(\gamma\) values. The table below shows the number of \(\mathbf{M}\)
that were unstable (\_unst) and stable (\_stbl) for the exponential
(Exp), beta, and gamma distributions.

\begin{longtable}[]{@{}lllllll@{}}
\toprule
S & Exp\_unst & Exp\_stbl & beta\_unst & beta\_stbl & gamma\_unst &
gamma\_stbl\tabularnewline
\midrule
\endhead
2 & 30 & 99970 & 30 & 99970 & 30 & 99970\tabularnewline
3 & 355 & 99645 & 355 & 99645 & 355 & 99645\tabularnewline
4 & 1506 & 98494 & 1512 & 98488 & 1516 & 98484\tabularnewline
5 & 3930 & 96070 & 3971 & 96029 & 4006 & 95994\tabularnewline
6 & 7738 & 92262 & 7844 & 92156 & 7918 & 92082\tabularnewline
7 & 13606 & 86394 & 13889 & 86111 & 13990 & 86010\tabularnewline
8 & 20535 & 79465 & 21002 & 78998 & 21114 & 78886\tabularnewline
9 & 28614 & 71386 & 29060 & 70940 & 29110 & 70890\tabularnewline
10 & 38375 & 61625 & 38388 & 61612 & 38441 & 61559\tabularnewline
11 & 48616 & 51384 & 48211 & 51789 & 47957 & 52043\tabularnewline
12 & 59254 & 40746 & 58025 & 41975 & 57473 & 42527\tabularnewline
13 & 68816 & 31184 & 66753 & 33247 & 66127 & 33873\tabularnewline
14 & 77721 & 22279 & 75149 & 24851 & 74222 & 25778\tabularnewline
15 & 84842 & 15158 & 82030 & 17970 & 81040 & 18960\tabularnewline
16 & 90365 & 9635 & 87809 & 12191 & 86600 & 13400\tabularnewline
17 & 94171 & 5829 & 91756 & 8244 & 90668 & 9332\tabularnewline
18 & 96978 & 3022 & 94977 & 5023 & 94176 & 5824\tabularnewline
19 & 98376 & 1624 & 97018 & 2982 & 96268 & 3732\tabularnewline
20 & 99218 & 782 & 98357 & 1643 & 97765 & 2235\tabularnewline
21 & 99678 & 322 & 99124 & 876 & 98746 & 1254\tabularnewline
22 & 99864 & 136 & 99599 & 401 & 99323 & 677\tabularnewline
23 & 99954 & 46 & 99783 & 217 & 99668 & 332\tabularnewline
24 & 99978 & 22 & 99920 & 80 & 99821 & 179\tabularnewline
25 & 99996 & 4 & 99967 & 33 & 99911 & 89\tabularnewline
26 & 99999 & 1 & 99979 & 21 & 99960 & 40\tabularnewline
27 & 99999 & 1 & 99990 & 10 & 99983 & 17\tabularnewline
28 & 100000 & 0 & 99999 & 1 & 99991 & 9\tabularnewline
29 & 100000 & 0 & 99999 & 1 & 99999 & 1\tabularnewline
30 & 100000 & 0 & 100000 & 0 & 100000 & 0\tabularnewline
31 & 100000 & 0 & 100000 & 0 & 99999 & 1\tabularnewline
32 & 100000 & 0 & 100000 & 0 & 100000 & 0\tabularnewline
\ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} &
\ldots{}\tabularnewline
50 & 100000 & 0 & 100000 & 0 & 100000 & 0\tabularnewline
\bottomrule
\end{longtable}

>>>>

The stability of \(\mathbf{A}\) versus \(\mathbf{M}\) was investigated
for each of the distributions of \(\gamma\) shown in panels b-d above.
The table below shows the number of \(\mathbf{A}\) versus \(\mathbf{M}\)
that were stable for the exponential (exp), beta, and gamma
distributions.

\begin{longtable}[]{@{}lllllll@{}}
\toprule
S & exp\_A & exp\_M & beta\_A & beta\_M & gamma\_A &
gamma\_M\tabularnewline
\midrule
\endhead
2 & 99965 & 99965 & 99974 & 99974 & 99977 & 99977\tabularnewline
3 & 99636 & 99635 & 99650 & 99648 & 99628 & 99628\tabularnewline
4 & 98576 & 98564 & 98482 & 98470 & 98508 & 98492\tabularnewline
5 & 96053 & 95971 & 96156 & 96096 & 96068 & 96004\tabularnewline
6 & 92036 & 91867 & 92104 & 91927 & 92233 & 92029\tabularnewline
7 & 86667 & 86333 & 86456 & 86070 & 86604 & 86161\tabularnewline
8 & 79670 & 79153 & 79392 & 78822 & 79393 & 78771\tabularnewline
9 & 71389 & 70911 & 70998 & 70529 & 71070 & 70548\tabularnewline
10 & 61674 & 61609 & 61794 & 61586 & 61265 & 61093\tabularnewline
11 & 51150 & 51935 & 51352 & 51924 & 51313 & 51951\tabularnewline
12 & 41209 & 42925 & 40954 & 42670 & 40708 & 42183\tabularnewline
13 & 30827 & 33462 & 30969 & 33770 & 31046 & 33522\tabularnewline
14 & 22203 & 25767 & 22208 & 25629 & 22342 & 25435\tabularnewline
15 & 15003 & 18877 & 15206 & 18913 & 15025 & 18464\tabularnewline
16 & 9613 & 13372 & 9504 & 13357 & 9418 & 12737\tabularnewline
17 & 5579 & 8967 & 5570 & 8976 & 5719 & 8487\tabularnewline
18 & 3104 & 5833 & 3048 & 5853 & 3060 & 5447\tabularnewline
19 & 1516 & 3578 & 1553 & 3633 & 1600 & 3185\tabularnewline
20 & 717 & 2067 & 799 & 2179 & 769 & 1862\tabularnewline
21 & 312 & 1196 & 310 & 1200 & 331 & 1039\tabularnewline
22 & 129 & 643 & 128 & 654 & 135 & 510\tabularnewline
23 & 48 & 321 & 48 & 359 & 57 & 242\tabularnewline
24 & 11 & 161 & 19 & 159 & 20 & 120\tabularnewline
25 & 1 & 59 & 5 & 81 & 7 & 45\tabularnewline
26 & 0 & 30 & 0 & 48 & 0 & 22\tabularnewline
27 & 0 & 10 & 0 & 16 & 0 & 6\tabularnewline
28 & 1 & 3 & 2 & 2 & 0 & 3\tabularnewline
29 & 0 & 2 & 0 & 0 & 0 & 0\tabularnewline
30 & 0 & 0 & 0 & 1 & 0 & 0\tabularnewline
31 & 0 & 0 & 0 & 1 & 0 & 0\tabularnewline
32 & 0 & 0 & 0 & 0 & 0 & 0\tabularnewline
\ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} &
\ldots{}\tabularnewline
50 & 0 & 0 & 0 & 0 & 0 & 0\tabularnewline
\bottomrule
\end{longtable}
